Exploring the linear separablity of syntactic and semantic information in BERT embeddings

### 2022-06-09 paper/paper.tex
adding conclusion

%Need to update this section to reflect the new dataset
% might change later if choose to run experiment in silver
We use the English Parallel Meaning Bank v4.0 \citep{pmbData} to test the linear separability of the semantic and syntactic information in word-level BERT embeddings. This dataset is consist of gold standard and silver standard of word-level semantic tags. The gold standard contains 5,438 sentences with annotations that are manually verfied while the silver standard contains 62,739 sentences with autogenerated annotations. All of our experiments will be conducted on gold standard data.

@@

\section{Conclusion}
\label{sec:conclusion}

Our probing experiment 
Though INLP successfully produces the desired guard function, it is worth also worth noting that our dataset is relatively small compared

@@

This is where our conclusion will go. This is where our future work will go.

>>>>

%Need to update this section to reflect the new dataset
% might change later if choose to run experiment in silver
We use the English Parallel Meaning Bank v4.0 \citep{pmbData} to test the linear separability of the semantic and syntactic information in word-level BERT embeddings. This dataset is consist of gold standard and silver standard of word-level semantic tags. The gold standard contains 5,438 sentences with annotations that are manually verified while the silver standard contains 62,739 sentences with autogenerated annotations. All of our experiments will be conducted on gold standard data.

@@

\section{Conclusion}
\label{sec:conclusion}
It has been established that linear classifer is successful in various linguistics probing tasks \citep{language-transfer}. Our experiment has confirmed linear classifer is robust for probing CCG tagging and semantics tagging on Parallel Meaning Bank \citep{pmbData}.

We employed INLP methods and successfully damaged the capablity of linear classifer to probe the designated tasks. After gained guard matrices that remove task specific informations from the embeddings, we examined the separablity of semantics and syntactic representation by evaluation tasks on various embeddings. Our analysis concluded:first, removing either syntactic or semantic representation will hurt probing tasks; second, syntactic task will be more dependent on semantic information than the opposite direction; last, BERT embeddings is more similar to syntactic representation than semantic representation.

Though INLP successfully produces the desired result, it is worth also worth noting that our dataset is relatively small compared to the number of parameters in linear classifier. In the future, we will expect this epxeriment to be reproduced at a larger scale so that the INLP method can be further validated.

@@

% This is where our conclusion will go. This is where our future work will go.
